\documentclass[11pt,letterpaper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{xcolor}

\definecolor{linkblue}{HTML}{0969DA}

\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue,
    pdfborder={0 0 0}
}

\pagestyle{empty}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
    {\LARGE\bfseries Ian Alloway} \\[4pt]
    727-470-8666 \,$\vert$\,
    \href{mailto:ian@allowayllc.com}{ian@allowayllc.com} \,$\vert$\,
    \href{https://linkedin.com/in/ianit}{linkedin.com/in/ianit} \,$\vert$\,
    \href{https://github.com/ianalloway}{github.com/ianalloway} \\[2pt]
    \href{https://ianalloway.xyz}{ianalloway.xyz} \,$\vert$\,
    Fairmont, WV (Remote-Friendly)
\end{center}

\vspace{12pt}

\today

\vspace{12pt}

Dear Hiring Manager,

\vspace{6pt}

I am writing to express my interest in joining your team. I am an applied AI engineer and data scientist who builds evaluation-driven software, production analytics systems, and decision-support products. I would welcome the opportunity to contribute technical depth, clear communication, and a strong bias toward shipping work that can be measured and improved.

\vspace{6pt}

I am currently Technical Staff at OpenAI, where I evaluate ChatGPT app development and agent-built software across engineering practices, logic, design taste, and overall product quality. That work has strengthened my ability to assess real-world code, surface failure modes, and give structured feedback that improves how models perform on software development tasks. As founder of Alloway LLC, I have delivered applied ML and analytics solutions end to end for sports, fintech, and business operations clients, including ML-driven tooling that improved client operational efficiency by 40\%.

\vspace{6pt}

My recent technical work also includes cybersecurity and hospitality analytics projects as a data science contractor at West Virginia University, and senior auditing work at Omniichain, where I built AI-powered anomaly detection over multi-chain blockchain data and helped reduce fraud incidents by 30\%. Public projects such as \href{https://github.com/ianalloway/juryrig}{juryrig}, \href{https://aiadvantagesports.com}{AI Advantage Sports}, and \href{https://github.com/ianalloway/repo-health}{repo-health} reflect the same focus: practical systems, strong engineering habits, and evidence you can inspect.

\vspace{6pt}

I completed a B.S. in Information Science at the University of South Florida in May 2026 (GPA 3.5, Magna Cum Laude) and will begin an M.S. in Artificial Intelligence at USF in August 2026. I am especially interested in roles where I can build useful AI products, improve model and system quality through evaluation, and work closely with engineering teams to ship reliable software.

\vspace{6pt}

Thank you for your time and consideration. I would be glad to discuss how my background fits your needs.

\vspace{12pt}

Sincerely,

\vspace{24pt}

Ian Alloway

\end{document}
